### 2020-05-26 writeup/transfer.tex
re structure

\section{Revisiting the Bias-Variance Trade-off for Multi-Task learning}
\label{sec_insight}

We revisit the classical bias-variance trade-off in the context of multi-task learning for linear regressions, in particular the setup of equation \eqref{eq_mtl}.
For the high-dimensional setting where the data size of the target task is a small constant times dimension $p$, we quantify the trade-off as a function of the task models $\set{\beta_i}_{i=1}^t$, data size $\set{n_i}_{i=1}^t$, and covariance matrices $\set{\Sigma_i}_{i=1}^t$.
After describing this technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
Our analysis reveals three contributing causes of negative transfer, including task model \textit{dissimilarity}, \textit{unbalanced} data size, and \textit{covariate shift}, which we describe in detail for the rest of the section.

\subsection{Determining Positive versus Negative Transfer}\label{sec_main}

@@

@@

@@

\section{Extending the Bias-Variance Trade-off to Transfer Learning}\label{sec_taskonomy}

>>>>

\section{A Technical Tool for Determining Positive versus Negative Transfer}
\label{sec_main}

We revisit the classical bias-variance trade-off in the context of multi-task learning for linear regressions, in particular the setup of equation \eqref{eq_mtl}.
For the high-dimensional setting where the data size of the target task is a small constant times dimension $p$, we quantify the trade-off as a function of the task models $\set{\beta_i}_{i=1}^t$, data size $\set{n_i}_{i=1}^t$, and covariance matrices $\set{\Sigma_i}_{i=1}^t$.

@@

To illustrate our intuition, we begin by considering the multi-task learning setting with one source task.
Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
We decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts (to be derived in Appendix \ref{app_proof_main})
\begin{align}
	\te_t(\hat{\beta}_t^{\MTL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_var}
\end{align}
where $\hat{v} = W_2 / W_1$ denotes the ratio of the output layer weights.
By comparing the bias and variance of $\te_t(\hat{\beta}_t^{\MTL})$ to $\te_t(\hat{\beta}_t^{\STL})$, we observe the following two effects, respectively.

\textbf{Model-shift bias.}
%We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
We term equation \eqref{eq_te_model_shift} as \textit{model-shift bias}, which captures how similar $\beta_1$ and $\beta_2$ are.
This part introduces a negative effect to multi-task learning.
The scaling term $\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
The output layer of each task scales the direction of $B$ suitably to fit the task.

\textbf{Variance reduction.}
Next, it is not hard to verify that equation \eqref{eq_te_var}, the variance of $\hat{\beta}_t^{\MTL}$, is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
This part introduces a positive variance reduction effect to performing multi-task learning.
Hence, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the trade-off between two effects:
(i) the positive effect from variance reduction;
(ii) the negative effect from model shift bias.

@@

\section{Theoretical Implications}
\label{sec_insight}
After describing this technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
Our analysis reveals three contributing causes of negative transfer, including task model \textit{dissimilarity}, \textit{unbalanced} data size, and \textit{covariate shift}, which we describe in detail for the rest of the section.

@@

\subsection{Extension to Transfer Learning}\label{sec_taskonomy}
